---
title: "text_analysis_cpc_congress_report"
author: "jjcheer"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Target

In this document, I'll crawl the content of the CPC congress report from the year 1977 (the 11th congress) to the year 2022 (the 20th congress). Using text analysis to compare the key words in each of the report to differentiate the key points in each of the 5 year interval.

## load pkgs

```{r}
library(tidyverse) # proving the pipe and facilitate the manipulation
library(rvest) # web crawl and parse
library(jiebaR) # Chinese word seperation.
library(wordcloud2) # word cloud
library(webshot) # use this pkg to store the word cloud in local
library(htmlwidgets) # use this pkg to store the word cloud in local
library(tidytext) # untoken the words, and generate tf-idf
library(ggh4x) # draw enhanced plots.
```

## The urls

Find the webpages which provides the content of the report, and stored in a tibble. Add a id column which denote the abbreviation of each of the congress. e.g., id = 11 means "shi yi da".(the eleventh congress)

```{r}
ccp_link <- tibble(
  id = c(11,12,13,14,15,16,17,18,19,20),
  p_link = c("https://fuwu.12371.cn/2012/09/25/ARTI1348541192153839.shtml",
             "https://fuwu.12371.cn/2012/09/27/ARTI1348712095996447.shtml",
             "https://fuwu.12371.cn/2012/09/25/ARTI1348562562473415.shtml",
             "https://fuwu.12371.cn/2012/09/26/ARTI1348641194361954.shtml",
             "https://fuwu.12371.cn/2012/09/27/ARTI1348726215537612.shtml",
             "https://fuwu.12371.cn/2012/09/27/ARTI1348734708607117.shtml",
             "https://fuwu.12371.cn/2012/06/11/ARTI1339412115437623.shtml",
             "https://www.12371.cn/2012/11/17/ARTI1353154601465336_all.shtml",
             "https://www.12371.cn/2017/10/27/ARTI1509103656574313.shtml",
             "https://www.12371.cn/2022/10/25/ARTI1666705047474465.shtml")
)
```

crawl the website, and store the content in the `p_content` column.

```{r}
ccp_report <- tibble(
  p_id = NULL,
  p_content = NULL
)

for (i in 1:10) {
  ccp_html <- read_html(ccp_link$p_link[i]) 
  (p_content <- ccp_html %>% 
      html_elements(".word") %>% 
      html_text2())
  
  ccp_report_row <- tibble(
    p_id = ccp_link$id[i],
    p_content
  )
  ccp_report <- rbind(ccp_report,ccp_report_row)
}

ccp_report
```

## Word cloud 

define the stop words you want to delete.
```{r}
stop_words_chinese <- tibble(
  words = c("的","地","得","和","要","我们",
            "是","了","中国","在"))
```

draw the word cloud of each of the congress report.

```{r}
for (i in 1:10) {

  tibble(segment(ccp_report$p_content[i],worker()))
  ccp_words <- tibble(segment(ccp_report$p_content[i],worker())) %>% 
  rename(words = `segment(ccp_report$p_content[i], worker())`)
  
  ccp_clean <- anti_join(ccp_words,stop_words_chinese)
  
  wordcloud2(freq(ccp_clean$words),shape = "star")
}
```

## the key words in each of the report, by tf-idf

Using `tf-idf`, get the key words in each of the report; Drawing the lollipops.

```{r}
wk <- worker()
ccp_corpus <- 
ccp_report %>% 
  mutate(words = map(p_content,segment,jieba = wk)) %>% 
  select(p_id,words)

ccp_table <-
ccp_corpus %>% 
  unnest(cols = c(words)) %>% 
  count(p_id, words)

## load tidytext, caculate tf-idf
library(tidytext)

ccp_tf_idf <- 
ccp_table %>% 
  bind_tf_idf(term = words, document = p_id, n = n )

## the keywords in each document
ccp_top10 <- 
ccp_tf_idf %>% 
  group_by(p_id) %>% 
  top_n(10,tf_idf) %>% 
  ungroup()

ccp_top10 %>%
  mutate(words = fct_reorder(words,n)) %>% 
  ggplot(aes(n,words)) %>% +
  geom_segment(aes(x = 0,
                   xend = n,
                   y= words,
                   yend = words)) +
  geom_point(shape = 21, size = 3, colour = "black", fill = "#FC4E07") +
  ggh4x::facet_wrap2(~ p_id,ncol = 5,scales = "free")+
  theme(text = element_text(family = "Songti SC"),
        axis.title=element_text(size=13,face="plain",color="black"),
        axis.text = element_text(size=10,face="plain",color="black"),
        legend.title=element_text(size=14,face="plain",color="black")
  )
```

